Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Add TBD
Add a comment

If we have evidence that does not fit into the user documentation, but
would rather be part of a design document, we use Hspec.  Hspec
provides an EDSL for defining specs.  A spec organizes evidence in a
tree structure (or a forest, to be accurate), and it is defined with \texttt{it} and
\texttt{describe}.

@@

\subsubsection{Hspec not provide a mechanism for expectations}
BDD frameworks use \emph{should} or \emph{must} instead of
\emph{assert} to express expectations.  Here is an example that uses
RSpec.

@@

\subsubsection{Hspec provides no mechanism to expect exceptions}
RSpec provides a mechanism to expect exceptions.

@@

>>>>

If we have evidence that does not fit into the user documentation, but
would rather be part of a design document, we use Hspec.

\begin{quote}
    Hspec was originally implemented by Trystan Spangler, and is now
    maintained and actively/further developed by one of the authors.

    \emph{sol: Do you think we should include this here? Is it
    relevant? If it is relevant, it would probably better fit in to
    the ``Introduction'', right?}
\end{quote}

Hspec provides an EDSL for defining specs.  A spec organizes evidence
in a tree structure (or a forest, to be accurate), and it is defined
with \texttt{it} and \texttt{describe}.

@@

%%%%%%%%%%%%%%%%
\subsubsection{Hspec does not provide a mechanism for expectations}
BDD frameworks use \emph{should} or \emph{must} instead of
\emph{assert} to express expectations.  Here is an example that uses
RSpec.

@@

%%%%%%%%%%%%%%%%
\subsubsection{Hspec provides no mechanism to expect exceptions}
RSpec provides a mechanism to expect exceptions.

@@

\begin{quote}
    \emph{TBD}
\end{quote}
